Intersection of non-matching grids of different dimensions

### 2016-09-28 paper_intersections.tex

  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)}  \nllabel{line:12edges}
  \For{unmarked edge $e$ of $S_4$}{
    $p=L[e]$\;
    \uIf{ $p$ is inside $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = \edgefaces($e$)
    } 
    \Else($p$ at the vertex $v$ of $S_4$){       
            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
    }    
    \uIf{ $p$ is on boundary of $S_3$ }{
         $p$ lies on edge or at vertex $x \in M_4$\;
         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
         \lElse{$F_g[f_0]=q$}
         $F_g[x]=-1$\tcp*{remove the backlink}
    }
    \Else{
         append $p$ to $I$\;
         $F_g[f_0]=p$\tcp*{overwrite the backlink}
         $F_p[p]=f_1$\;
         mark all edges coincident with $p$
    }   
  }

@@

Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
The loop produces IPs in the interior of $S_3$ and possibly those IPs with special position on vertex or edge of $S_4$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
IP on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
uses the sign of the intersection to return the pair of faces ordered correctly. 
Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.

>>>>

  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)}  \nllabel{line:12edges}
  \For{unmarked edge $e$ of $S_4$}{
    $p=L[e]$\;
    \uIf{ $p$ is inside $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = \edgefaces($e$)
    } 
    \Else($p$ at the vertex $v$ of $S_4$){       
            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
            \nllabel{line:mark_edges}
            mark all edges coincident with $p$
    }    
    \uIf{ $p$ is on boundary of $S_3$ }{
         $p$ lies on edge or at vertex $x \in M_4$\;
         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
         \lElse{$F_g[f_0]=q$}
         $F_g[x]=-1$\tcp*{remove the backlink}
    }
    \Else{
         append $p$ to $I$\;
         $F_g[f_0]=p$\tcp*{overwrite the backlink}
         $F_p[p]=f_1$\;         
    }   
  }

@@

Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
The loop produces IPs in the interior of $S_3$ and possibly those IPs with special position on vertex or edge of $S_4$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
IP on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
uses the sign of the intersection to return the pair of faces ordered correctly. 
Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection point they are degenerate and 
not processed anyway.
